### 2022-06-28 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@dd96400fd33ea3c63c56143b8e9b6e484ba54afa 🚀

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{Trivariate additive mapping of the components of risk in the
red/green/blue, where high virus sharing is encoded in the blue channel,
host phylogenetic diversity in the green channel, and compositional
uniqueness in the red channel. The main driver of emergence risk
(possibility of spatially overlapped but coevolutionarily indepent
host-viral dynamics) corresponds to low viral sharing, \emph{i.e.}
pixels around yellow.}\label{fig:trivariate}
}
\end{figure}

>>>>

\begin{figure}
\hypertarget{fig:trivariate}{%
\centering
\includegraphics{figures/risk_trivariate.png}
\caption{Trivariate additive mapping of the components of risk. Viral
sharing runs from yellow (low) to blue (high); host phylogenetic
diversity runs from pink (low) to high (green) channel, and
compositional uniqueness runs from cyan (low) to red (high). The GMTC
suggests that the highest evolutionary potential for emergence exists in
unique and diverse host communities with low viral sharing, \emph{i.e.}
pixels around yellow.}\label{fig:trivariate}
}
\end{figure}
